An Embedding Framework for Consistent Polyhedral Surrogates

### 2020-02-21 journal/poly-embed.tex
Pushing the mess that I've made in the properties section

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{[PROPOSED ADDITION: #1]}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{[BTW: #1]}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

@@

  For each $r\in\R$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
  Observe that, by definition of the Bayes risk and $\Gamma$, for all $u\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(u)})$ if and only if $u\in\Gamma(p)$.
  Thus, the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports $E_L = E_\ell$ at the point $(p_r,-\inprod{p_r}{L(u_r)})$, and thus does so at the entire facet $\{(p,-\inprod{p}{L(u_r)}) : p\in\gamma_r\}$; by the above, $u_r \in \Gamma(p)$ for all such distributions as well.
  We conclude that $u_r \in \Gamma(p) \iff p \in \gamma_r \iff r \in \gamma(p)$, satisfying condition~\eqref{eq:embed-loss} for $\varphi : r \mapsto u_r$.
  To see that the loss values match, we merely note that the supporting hyperplanes to the facets of $E_L$ and $E_\ell$ are the same, and the loss values are uniquely determined by the supporting hyperplane.
  (In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.)
\end{proof}

@@

\btw{Cut summary for now (Why is this cool?)}
\jessiet{The commented out section is now in colt-20, but I'm adding a bit to say why this is cool.}
We will see that embedding implies the existence of a consistent surrogate and link, so this result tells us that, for discrete losses, the embedding framework is sufficient to understand the existence of consistent surrogates for the given loss.
Even if there is a smooth surrogate for a given discrete loss, there is also a polyhedral loss that is calibrated for the given loss.
What's more is that there is a polyhedral \emph{embedding} that is calibrated for the discrete loss.

@@

@@

\jessie{Everything below here is added from the COLT-19 version}

@@

\begin{proposition}
	Let $L$ elicit $\Gamma:\simplex \toto \reals^d$ which embeds a finite property $\gamma$.
	Then there is a calibrated link from $\Gamma$ to $\gamma$.
\end{proposition}
\begin{proof}
	Let $\gamma: \simplex \toto \R$.
	Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r \in \R\}$.
	We conclude that for any $u \in \reals^d$, there is a calibrated link from $\Gamma$ to $\gamma$.\jessie{define calibrated link for properties?}
	\jessie{TODO}
\end{proof}
\jessie{Not sure what we want to say about calibrated links, if anything.}

@@

\jessie{Other results on refined properties? Assuming we don't want the embedding dimension conjecture brought up on 02.03.2020 in here.}
\begin{conjecture}
	Let $\gamma'$ be a refinement of $\gamma$.
	Then an embedding for $\gamma'$ can also embed $\gamma$.
\end{conjecture}

>>>>

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{[BTW: #1]}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

@@

  For each $r\in\R$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
  Observe that, by definition of the Bayes risk and $\Gamma$, for all $u\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(u)})$ if and only if $u\in\Gamma(p)$.
  Thus, the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports $E_L = E_\ell$ at the point $(p_r,-\inprod{p_r}{L(u_r)})$, and thus does so at the entire facet $\{(p,-\inprod{p}{L(u_r)}) : p\in\gamma_r\}$; by the above, $u_r \in \Gamma(p)$ for all such distributions as well.
  We conclude that $u_r \in \Gamma(p) \iff p \in \gamma_r \iff r \in \gamma(p)$, satisfying condition~\eqref{eq:embed-loss} for $\varphi : r \mapsto u_r$.
  To see that the loss values match, we merely note that the supporting hyperplanes to the facets of $E_L$ and $E_\ell$ are the same, and the loss values are uniquely determined by the supporting hyperplane.
  (In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.)
\end{proof}
\begin{proof}[Via properties]
	\jessie{($L$ embeds $\ell \implies \risk{L} = \risk{\ell}$.)  $L$ embeds $\ell$ implies $\Gamma$ embeds $\gamma$, which is finite as $\ell$ is discrete.  By Prop 3, then we have $\{\gamma_r : r \in \R\} = \trim(\Gamma) = \{\Gamma_u : u \in \U \subset \reals^d \}$, where $\U$ is finite. Since $L$ embeds $\ell$}
	\jessie{$(\risk{L} = \risk{L} \implies L$ embeds $\ell$).  $\risk{L} = \risk{\ell}$ implies $\{\gamma_r : r \in \R\} = \trim(\Gamma)$, and therefore $\Gamma$ embeds $\gamma$, satisfying the first two conditions.  For the matching losses, this follows from the risks being equal...?}
\end{proof}

@@

\btw{Cut summary for now (Why is this cool?)}
\jessiet{The commented out section is now in colt-20, but I'm adding a bit to say why this is cool.}
\proposedadd{We will see that embedding implies the existence of a consistent surrogate and link, so this result tells us that, for discrete losses, the embedding framework is sufficient to understand the existence of consistent surrogates for the given loss.
Even if there is a smooth surrogate for a given discrete loss, there is also a polyhedral loss that is calibrated for the given loss.
What's more is that there is a polyhedral \emph{embedding} that is calibrated for the discrete loss.}

@@

\section{Embedding properties}\label{sec:embed-props}
\jessie{Forked from appendix... if we adopt this, we should delete some of the content from the appendix.}

While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
\begin{definition}\label{def:prop-embed}
	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
\end{definition}

By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
\proposedadd{However, we should observe that this statement is not an ``if and only if'' because property embedding does not capture the requirement of matching losses on embedded points.}

It is often convenient to work directly with properties and set aside the losses which elicit them.
We begin with the notion of redundancy.
\begin{definition}[Finite property, non-redundant]
	A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
	$\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
\end{definition}

When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the expected loss.
As results in property elicitation typically assume properties are non-redundant (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), it is useful to consider a transformation which removes redundant level sets.
We capture this transformation as the trim operator presented below.

%\btw{RF: Note for later: should be able to show that the union of trim is the simplex.\jessie{This is part of the proposition statement 2 now.}}
%Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$; this is a corollary of Proposition~\ref{prop:embed-trim}.

Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses. \jessie{I think this is what's throwing me off 2.20.20}
The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
The second is closely related to the definition of the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).

We now state a useful result for proving the existence of an embedding loss, which shows remarkable structure of embeddable properties, and the properties that embed them.
First, we conclude that any embeddable property must be elicitable.
We also conclude that if $\Gamma$ embeds $\gamma$, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
In other words, $\Gamma$ is exactly the property $\gamma$, just with other reports filling in the gaps between the embedded reports of $\gamma$.
(When working with convex losses, these extra reports are typically the convex hull of the embedded reports.)
In this sense, we can regard embedding as a slight departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trim(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.

	1 $\Rightarrow$ 2:
        \jessie{Intuition: $\Gamma$ embeds $\gamma$ implies their level sets are the same on facets, and $\trim(\Gamma)$ gets rid of any redundancies in $\Gamma$'s level sets.  Moreover, $\cup \trim(\Gamma) = \simplex$ since for all $\theta \in \trim(\Gamma)$, there is a $\gamma_r \in \gamma(\simplex)$ so that $\theta = \gamma_r$ and $\gamma$ is non redundant.}
        \jessie{Loss intuition: If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  Therefore, $\risk{L} = \risk{\ell}$ is polyhedral. }
	Since $\Gamma$ embeds $\gamma$, we know that $\gamma_r = \Gamma_{\varphi(r)}$.
	If we can show $\trim(\Gamma) = \{\Gamma_{\varphi(r)}\}_{r \in \R}$, then it suffices to see the result in terms of $\{\Gamma_{\varphi(r)}\}_{r \in \R}$.
	\hrule
	First, to see $\trim(\Gamma) \subseteq \Gamma_{\varphi(\R)}$.
	Take $\theta \in \trim(\Gamma)$.
	There must be some $u$ such that $\theta = \Gamma_u$.

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	Take some $u \not \in \varphi(\R)$.
	We want to show that there exists a $r \in \R$ such that $\Gamma_u \subseteq \Gamma_{\varphi(r)}$, and therefore, $\Gamma_u \not \in \trim(\Gamma)$.

	Consider any $p$ such that $p \in \Gamma(u)$.
	Since $\gamma$ is nondegenerate, we know $p \in \gamma(r)$ for some $r \in \R$, and by $\Gamma$ embedding $\gamma$, we also have $p \in \Gamma(\varphi(r))$.
	Therefore, $\Gamma(u) \subseteq \Gamma(\varphi(r))$.
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	Next, to see $\Gamma_{\varphi(\R)} \subseteq \trim(\Gamma)$.
	Take $r \in \R$, and call $\theta = \Gamma_{\varphi(r)} = \gamma_r$.
	As $\gamma$ is nonredundant, we know there is no $r' \in \R$ such that $\gamma_{r'} = \Gamma_{\varphi(r')} \subseteq \theta$, and therefore $\theta \in \trim(\Gamma)$.
	\hrule
	Now that we have established $\trim(\Gamma) = \Gamma_{\varphi(\R)}$, we we show the result.
	As $\R$ is a finite set, so is $\Gamma_{\varphi(\R)}$ as it is finitely generated.
	Moreover, $\gamma$ is nondegenerate, we then have $\cup_\R \Gamma_{\varphi(r)} = \cup_\R \gamma_r = \simplex$.

	2 $\Rightarrow$ 3: \jessie{Intuition: Each $\theta \in \trim(\Gamma)$ is full dimensional.  Take $\Theta = \trim(\Gamma)$.}

    \hrule \jessie{New}
    Each $\theta_i \in \Theta$ has some $u_i$ such that $\theta_i = \Gamma_{u_i}$.
    As $\cup \trim(\Gamma) = \cup_i \theta_i = \cup_i \Gamma_{u_i}$, we then have $\cup \Gamma_{u_i} = \simplex$

    If $\Gamma_{u_i}$ was not full-dimensional, then it would not be in $\trim(\Gamma)$

    \hrule

    Let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
	Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
	We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
	The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
	Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
	Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.

	3 $\Rightarrow$ 1: \jessie{Intuition: Take $\gamma = \Gamma|_{\varphi(\R)}$.}
        Let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
	For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
	Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
\end{proof}
\begin{proof}[Original]
	Let $L$ elicit $\Gamma$.

\jessie{Added from COLT-19 but not discussed in COLT-20}

\begin{proposition}
	Let $L$ elicit $\Gamma:\simplex \toto \reals^d$ which embeds a finite property $\gamma$.
	Then there is a calibrated\jessie{formerly separated?} link from $\Gamma$ to $\gamma$.
\end{proposition}
\begin{proof}
	Let $\gamma: \simplex \toto \R$.
	Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r \in \R\}$.
	We conclude that for any $u \in \reals^d$, there is a calibrated link from $\Gamma$ to $\gamma$.
\end{proof}

\jessie{Other results on refined properties? Assuming we don't want the embedding dimension conjecture brought up on 02.03.2020 in here.}
\begin{conjecture}
	Let $\gamma'$ be a refinement of $\gamma$.
	Then a loss $\ell$ embedding for $\gamma'$ also embeds $\gamma$. \jessie{Not quite.  I think something similar is true, but we need more assumptions. See below for a related statement though.}
\end{conjecture}

\begin{proposition}
	Take $\prop{\ell} =: \gamma : \simplex \toto \R$ and $\prop{\ell'} =:\gamma' : \simplex \toto \R'$.
	If $\gamma'$ refines $\gamma$ and $L'$ is calibrated with respect to  the discrete loss $\ell'$, then there exists a link $\psi$ so that $(L', \psi)$ is calibrated with respect to $\ell$.
\end{proposition}
\begin{proof}
	Let us construct the link $\psi$ such that, for all $r' \in \R'$ consider $r \in \R$ so that $\gamma'_{r'} \subseteq \gamma_r$.
	Define $\psi$ so that $\psi'(u) = r' \implies \psi(u) = r$.

	To see this link and surrogate are calibrated with respect to $\ell$, consider that for any fixed $p \in \simplex$, $\{u \in \reals^d : \psi(u) \not \in \gamma(p)\} \subseteq \{u \in \reals^d : \psi'(u) \not \in \gamma'(p)\}$, which in turn implies that the infimum over the first term of the expected loss is at least the infimum over the second term, which is strictly greater than the Bayes Risk of $L'$ at $p$ by calibration of $(L', \psi')$.

	\jessiet{Probably need to be more thorough on the subset argument.}
	That is, 
	\begin{align*}
	\{u \in \reals^d : \psi(u) \not \in \gamma(p)\} &\subseteq \{u \in \reals^d : \psi'(u) \not \in \gamma'(p)\}\\
	\implies
	\inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L'(u)} &\geq \inf_{u \in \reals^d : \psi'(u) \not \in \gamma'(p)} \inprod{p}{L'(u)} > \inf_u \inprod{p}{L'(u)}\\
	\implies 		\inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L'(u)} &> \inf_u \inprod{p}{L'(u)}~.~
	\end{align*}
	Thus, as $p$ is arbitrary, we observe $(L', \psi)$ is calibrated with respect to $\ell$.
\end{proof}

\iffalse
\begin{conjecture}
	Let $\gamma'$ refine $\gamma = \prop{\ell}$ and $L'$ embeds $\gamma'$ by the injection $\varphi'$.
	Define $\phi : \R \to \R'$ such that $\phi(r) = r' \implies \gamma'_{r'} \subseteq \gamma_r$.
	Let $\varphi:\R \to \reals^d = \phi \circ \varphi'$
	Then $(-\risk{L'|_{\varphi(R)}})^*$ embeds $\ell$.
\end{conjecture}
\fi

@@

\jessie{Added from COLT-19 but not discussed in COLT-20}

@@

\begin{proposition}
	Let $L$ elicit $\Gamma:\simplex \toto \reals^d$ which embeds a finite property $\gamma$.
	Then there is a calibrated link from $\Gamma$ to $\gamma$.
\end{proposition}
\begin{proof}
	Let $\gamma: \simplex \toto \R$.
	Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r \in \R\}$.
	We conclude that for any $u \in \reals^d$, there is a calibrated link from $\Gamma$ to $\gamma$.\jessie{Added definition for calibrated link for properties above.}
\end{proof}
\jessie{Not sure what we want to say about calibrated links, if anything.}

@@

\jessie{Other results on refined properties? Assuming we don't want the embedding dimension conjecture brought up on 02.03.2020 in here.}
\begin{conjecture}
	Let $\gamma'$ be a refinement of $\gamma$.
	Then a loss $\ell$ embedding for $\gamma'$ also embeds $\gamma$. \jessie{Not quite.  I think something similar is true, but we need more assumptions. See below for a related statement though.}
\end{conjecture}

\begin{proposition}
	Take $\prop{\ell} =: \gamma : \simplex \toto \R$ and $\prop{\ell'} =:\gamma' : \simplex \toto \R'$.
	If $\gamma'$ refines $\gamma$ and $L'$ is calibrated with respect to  the discrete loss $\ell'$, then there exists a link $\psi$ so that $(L', \psi)$ is calibrated with respect to $\ell$.
\end{proposition}
\begin{proof}
	Let us construct the link $\psi$ such that, for all $r' \in \R'$ consider $r \in \R$ so that $\gamma'_{r'} \subseteq \gamma_r$.
	Define $\psi$ so that $\psi'(u) = r' \implies \psi(u) = r$.

	To see this link and surrogate are calibrated with respect to $\ell$, consider that for any fixed $p \in \simplex$, $\{u \in \reals^d : \psi(u) \not \in \gamma(p)\} \subseteq \{u \in \reals^d : \psi'(u) \not \in \gamma'(p)\}$, which in turn implies that the infimum over the first term of the expected loss is at least the infimum over the second term, which is strictly greater than the Bayes Risk of $L'$ at $p$ by calibration of $(L', \psi')$.

	\jessiet{Probably need to be more thorough on the subset argument.}
	That is, 
	\begin{align*}
		\{u \in \reals^d : \psi(u) \not \in \gamma(p)\} &\subseteq \{u \in \reals^d : \psi'(u) \not \in \gamma'(p)\}\\
		\implies
		\inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L'(u)} &\geq \inf_{u \in \reals^d : \psi'(u) \not \in \gamma'(p)} \inprod{p}{L'(u)} > \inf_u \inprod{p}{L'(u)}\\
		\implies 		\inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L'(u)} &> \inf_u \inprod{p}{L'(u)}~.~
	\end{align*}
	Thus, as $p$ is arbitrary, we observe $(L', \psi)$ is calibrated with respect to $\ell$.
\end{proof}

\begin{conjecture}
	Let $\gamma'$ refine $\gamma = \prop{\ell}$ and $L'$ embeds $\gamma'$ by the injection $\varphi'$.
	Define $\phi : \R \to \R'$ such that $\phi(r) = r' \implies \gamma'_{r'} \subseteq \gamma_r$.
	Let $\varphi:\R \to \reals^d = \phi \circ \varphi'$
	Then $(-\risk{L'|_{\varphi(R)}})^*$ embeds $\ell$.
\end{conjecture}
